Inter-task effects induce bias in crowdsourcing

### 2014-08-04 docs/publications/2014.08_HCOMP/_man.tex
make version for hcomp PhD consortium submission

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[a4paper]{report}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
\usepackage{scrextend}
\usepackage{graphicx}

@@

\begin{document}
\maketitle
\section*{Abstract}
Microtask platforms like Amazon Mechanical Turk provide a cheap and fast means
to engage participants for scientific reasearch.  
Workers on such platforms prefer to work on batches of tasks of the same 
type[***], so we investigate the potential for the content of earlier tasks 
to influence worker performance in later tasks, which we call ``inter-task'' 
effects.  
Existing research investigates the impact of various design factors, such as 
``framing'', on the quality of crowdsourced content, but does not, to 
our knowledge, address inter-task effects.  
We employ a canonical image-labeling task on the Amazon Mechanical Turk 
platform, to measure both inter-task and framing effects, in terms of their 
impact to the content and specificity of the labels workers provide.
We also introduce an algorithmic definition of priming, which measures the 
worst-case bias that priming effects introduce into crowdsourced content.
We find that inter-task effects produce a much stronger impact than framing, 
and find that our algorithmic definition yields a powerful, generalized measure
for priming effects when combined with machine learning algorithms.

\section*{Significance Statement}
\section*{Introduction}

@@

To characterize the effects of inter-task priming, we present a novel  
\textit{algorithmic definition of priming}, along with a general method 
for measuring priming effects using machine learning algorithms.  
Existing work on priming effects focuses on the internal psychological 
mechanisms of priming[***], but here we are interested in how the treatment of 
workers can impact an application of human computation. This leads us to 
quantify priming in terms of the algorithmic distinguishability of priming
treatments.

In the present work, we investigate inter-task priming using image-labeling 
tasks on the AMT platform.  
(***why we are using image labeling as prototypical task***) 
Each worker is required to label ten images 
featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{final set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
Each worker is randomly assigned one of three initial sets, but the final set
of images is always the same.  We analyze the effect that the assignment of 
initial set has on workers' attribution of labels to the final set.  We 
measure effects using our novel approach, as well as looking for changes in 
the content of labels and label specificity based on an ontology we 
developed for that purpose.

As a point of comparison, we subject some groups of workers to a kind of
\textit{framing}: we disclose a fictitious, semantically-loaded name for 
requester funding the tasks.
The names were chosen to suggest the requester's interest in 
a specific aspect of the image content.  One might reasonably expect that this 
would orient workers to provide a greater quantity and specificity of labels 
which relate to this ``preferred'' content[***].

@@

In psychology, the effects of priming are usually measured in terms of a 
change in the  
speed or accuracy of responses in a task, or in the ability to recognize a 
stimulus object (e.g. a spoken word or an image) when the object is noisier, 
fainter, or briefer [***].  Methods are also employed to measure processes
in the brain of the participant, such as by fMRI[***].  These approaches are 
well-suited to studying the underlying psychological mechanisms at work.

@@

In practice, some particular classifier $\mathcal{C}$ must be used and a 
statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
theoretical value $\theta$ from the definition, because there might 
exist some other classifier $\mathcal{C}'$ with 
$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
Here, we use a Naive Bayes classifier because it simple and performs well 
across a broad range of classification tasks[***].

@@

\subsection*{Experimental Setup}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

	\begin{addmargin}[4em]{4em}
	\caption{ \footnotesize{ 
		Workers were uniformly randomly assigned to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
	}}
	\end{addmargin}
	\label{table:1}
\end{table}

@@

\begin{figure}
	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
	\caption{ \footnotesize{
		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
		various treatments.  The difference in priming between each pair of 
		treatments 
		was determined by cross-validation of a Naive Bayes classifier trained
		to classify workers based on the labels they attributed to the first
		image of the final image set. Each panel compares a basis treatment,
		indicated above the panel, to various treatments indicated on the
		abscissa.  We can conclude, with 95\% confidence, that the classifier
		is performing better than chance when $\hat{\theta}_\text{NB}$ 
		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
		the calculation of this confidence threshold.
	}}
\end{figure}

@@

To this end, we constructed an ontology of labels attributed to the final 
images.  The ontology was constructed as a directed acyclic graph, with edges 
pointing from more general labels to more specific ones.
For example, our ontology contains the path \texttt{food} $\to$ 
\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
provide more detail about the construction of the ontology in the 
\textbf{Materials and Methods} section.

@@

\paragraph{Earlier tasks influenced workers' level of specificity.} 
\begin{figure}
	\begin{center}
		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
	\caption{\footnotesize{
		\textbf{A}) Percent label composition (culture- vs food-oriented 
		labels) for 
		various images and treatments.  
		\textbf{B}) Relative specificities of treatments
		indicated along the abscissa compared to those indicated above the 
		plot.  The size of the bar indicates how much more specific
		the labels from one treatment are compared to the other, and points 
		toward in the direction of the more specific treatment.
	}}
	\end{center}
\end{figure}

@@

\paragraph{Inter-task effects ``wash out'' quickly.}  
\begin{figure}
	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
	\caption{\footnotesize{
		\textbf{A}) Difference in priming between \textsc{AMBG} and 
		$\textsc{CULT}_{img}$ measured based on the accuracy of a Naive Bayes 
		classifier during cross-validation, when trained on labels from the
		test images indicated along the abscissa.
		\textbf{B}) Excess cultural orientation of labels attributed to
		the test images indicated on the abscissa, by workers from
		$\textsc{CULT}_{img}$ relative to those attributed by workers from
		\textsc{AMBG}, calculated using \textbf{Eq. 3}.
	}}
\end{figure}
At this point we have 
investigated the inter-task effects induced on only the first image of the 
final image set.  This is because, as mentioned, the effects are strongest on 
for first image.  We now examine how the inter-task effects vary as workers 
proceed through the images in the final set.  Since the final images are the
same for all treatments, it would stand to reason that the inter-task effects
induced by the initial image sets would fade away, being washed out by the
inter-task effects of the final set.

@@

\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}

@@

\paragraph{Inter-task similarity encourages more specific labels.}
For the next part of the analysis, it will be useful to speak of the
``similarity'' between two image sets. In general, the characterization of 
image content 
is deeply complex and has been approached from the perspectives of 
art\cite{panofsky1939studies,shatford1986analyzing},
psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.
Furthermore, the perception of \textit{similarity} is a particularly subtle 
psychological phenomenon.  For example, a figure $A$ can appear simultaneously
both \textit{more} and \textit{less} similar to an object $C$ than some other 
object $B$[***].

@@

\begin{table}
\centering
\begin{tabular}{ l  d  s s s s}

@@

\end{tabular}
\caption{\footnotesize{
	Number of unique labels attributed to each image set, and their
	similarities based on \textbf{Eq. 4} 
}}
\label{table:2}
\end{table}

@@

This suggests that labeling a series of images that are similar to 
one another might encourage workers to use more specific terminology.
Such a phenomenon would be consistent with the psychological mechanism known 
as \textit{negative priming}.  Negative priming occurs when a person becomes 
desensitized to non-salient stimuli to which she is repeatedly 
exposed [***].  Consider that workers who initially 
labeled the ambiguous image set had already seen five images showing 
prepared meals once they labeled the first test image.  At that point,
a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
salient, since they do not distinguish the image from those she had seen 
already.

@@

\subsection*{Materials and Methods}

\textbf{AMT Tasks.} The task described in \textbf{Experimental Setup}
was served to 900 workers, who were uniformly randomly assigned to
treatments.  Each treatment had at least 126 task completions.  To obtain 
uniformly sized treatments, we randomly selected 126 samples from each 
treatment. Workers were
only allowed to participate once and could not see the initial or final 
images, nor the funder names when previewing the task.

\textbf{Naive Bayes Classifier.}
The features provided to the Naive Bayes classifier consisted of the labels
that the worker provided along with the image and specific location in which 
the label was entered
(each image had five distinct label inputs).  Thus, \texttt{wine} occurring in 
position 1 of image 2 would be considered as a distinct feature from 
\texttt{wine} occurring in position 2 of image 2. The classifier 
had better performance when this distinction was made.

\textbf{Building the ontology of terms.}  The ontology was built manually
by the experimenters, starting from the corpus of labels. Labels occurring only 
once were discarded.  We created the root classes \texttt{activity}, 
\texttt{adjective}, \texttt{culture}, 
\texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
given top-level status because they were prominently represented in the corpus.
Whenever one label was judged to be a more specific case of another, a
directed edge was drawn from the more general to the more specific. This
judgment call was made by the experimenters.  However, the labels from all 
treatments were aggregated before assembling the ontology,  to 
ensure that the ontology construction would not be affected by 
knowledge of the treatments from which labels originated. 
Labels which were judged to be roughly synonymous were treated as identical,
and labels judged to be misspellings were corrected.

\textbf{Statistical significance of $\theta_\text{NB}$.}
We test the significance two population's measured $\theta_\text{NB}$ against 
the null hypothesis that that the two populations are in fact identical:
\begin{align}
	\mathbf{H_0}: \theta_\text{NB} = 0 \\
	\mathbf{H_1}: \theta_\text{NB} > 0
\end{align}
If the populations are in fact identical, then the probability that the 
classifier correctly classifies a worker is $\frac{1}{2}$. Let $K$ be a random
variable which denotes the number of correct classifications when the 
classifier is challenged to classify a total of $n$ workers during 
cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
is:
\begin{align}
	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
\end{align}
We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
is greater than or equal to a critical value, $\theta_\text{NB}^*$:
\begin{align}
	\theta^*_\text{NB} = \frac{2k^*}{n} - 1
\end{align}
where $k^*$ is the smallest integer in $\{0,\dots,n\}$ that satisfies 
\begin{align}
	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
\end{align}
For a 5-fold cross-validation with non-overlapping test sets containing 25 
workers ($n = 125$), and a significance of $\alpha = 0.05$, we
have $k^*=73 \implies \theta_\text{NB}^* = 0.168$.

\textbf{Statistical significance of relative specificity.}
We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
of two treatments.  To analyze relative specificity statistically,
we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
definition.  Let the specificity of a worker $u$ relative to a 
\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, be the expected 
relative specificity between $u$ and a worker uniformly sampled from 
$\mathcal{V}$:

\begin{align}
	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
		\label{eq:basis-specificity}
\end{align}
where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
subscript the expectation operator with $V$ to indicate 
that the expectation is taken over the distribution of $V$.  Then, the 
relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
written as:
\begin{align}
	S(\mathcal{U},\mathcal{V}) = 
		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
		\label{eq:treatment-specificity}
\end{align}
where $U$ is a random, uniformly sampled worker from $\mathcal{U}$.  This 
yields 
estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
as shown below (note that 
\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
equivalent to \textbf{Eq.~\ref{eq:specificity}}):

\begin{align}
	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
		\label{eq:basis-specificity-estimator} \\
		\hat{S}(\mathcal{U},\mathcal{V}) 
		&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} \hat{S}_V(u),
		\label{eq:treatment-specificity-estimator} \\
		\text{Var}_V\{\hat{S}_V(u)\} 
			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
		\label{eq:basis-specificity-variance} \\
		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
		\label{eq:treatment-specificity-variance}
\end{align}
\td{There are problems with this.  I'm still trying to figure out how to
	calculate the variance properly.}
$\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
\textbf{Equations \ref{eq:basis-specificity-estimator}} through 
\textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
\begin{align}
	\begin{matrix}
		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
	\end{matrix}
\end{align}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
	\caption{Testing image set. These images were presented to all workers in 
		the order shown after the priming set of images.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
	\caption{ Ambiguous image set. These images were presented to workers from 
		certain treatments (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
	\caption{Cultural image set. These images were presented to workers from 
		certain treatments (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
	\caption{ Ingredients image set. These images were presented to workers 
		from certain treatments (see \textbf{Table 1}) in the order shown.}
\end{figure}
\section*{Acknowledgments}
\section*{References}
\begingroup
\renewcommand{\chapter}[2]{}
\bibliography{newbib.bib}
\endgroup
\bibliographystyle{plain}

\end{document}

>>>>

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[letterpaper,twocolumn]{article}
\usepackage[hmargin=0.75cm,vmargin=0.75cm]{geometry}
\usepackage{scrextend}
\usepackage{graphicx}

@@

\begin{document}
\maketitle
\section*{Abstract}
Microtask platforms like Amazon Mechanical Turk provide a cheap and fast means
to engage participants for scientific reasearch.  
Workers on such platforms prefer to work on batches of tasks of the same 
type, so we investigate the potential for the content of earlier tasks 
to influence worker performance in later tasks, which we call ``inter-task'' 
effects.  
Existing research investigates the impact of various design factors, such as 
``framing'', on the quality of crowdsourced content, but does not, to 
our knowledge, address inter-task effects.  
We employ a canonical image-labeling task on the Amazon Mechanical Turk 
platform, to measure both inter-task and framing effects, in terms of their 
impact to the content and specificity of the labels workers provide.
We also introduce an algorithmic definition of priming, which measures the 
worst-case bias that priming effects introduce into crowdsourced content.
We find that inter-task effects produce a much stronger impact than framing, 
and find that our algorithmic definition yields a powerful, generalized measure
for priming effects when combined with machine learning algorithms.

\section*{Introduction}

@@

To characterize the effects of inter-task priming, we present a novel  
\textit{algorithmic definition of priming}, along with a general method 
for measuring priming effects using machine learning algorithms.  
Existing work on priming effects focuses on the internal psychological 
mechanisms of priming, but here we are interested in how the treatment of 
workers can impact an application of human computation. This leads us to 
quantify priming in terms of the algorithmic distinguishability of priming
treatments.

In the present work, we investigate inter-task priming using image-labeling 
tasks on the AMT platform.  
Each worker is required to label ten images 
featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{final set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
Each worker is randomly assigned one of three initial sets, but the final set
of images is always the same.  We analyze the effect that the assignment of 
initial set has on workers' attribution of labels to the final set.  We 
measure effects using our novel approach, as well as looking for changes in 
the content of labels and label specificity based on an ontology we 
developed for that purpose.

As a point of comparison, we subject some groups of workers to a kind of
\textit{framing}: we disclose a fictitious, semantically-loaded name for 
requester funding the tasks.
The names were chosen to suggest the requester's interest in 
a specific aspect of the image content.  One might reasonably expect that this 
would orient workers to provide a greater quantity and specificity of labels 
which relate to this ``preferred'' content.

@@

In psychology, the effects of priming are usually measured in terms of a 
change in the  
speed or accuracy of responses in a task, or in the ability to recognize a 
stimulus object (e.g. a spoken word or an image) when the object is noisier, 
fainter, or briefer.  Methods are also employed to measure processes
in the brain of the participant, such as by fMRI.  These approaches are 
well-suited to studying the underlying psychological mechanisms at work.

@@

In practice, some particular classifier $\mathcal{C}$ must be used and a 
statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
theoretical value $\theta$ from the definition, because there might 
exist some other classifier $\mathcal{C}'$ with 
$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
Here, we use a Naive Bayes classifier because it simple and performs well 
across a broad range of classification tasks.

@@

\subsection*{Experimental Setup}

\begin{figure*}
	\centering{
	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
	\caption{ \footnotesize{
		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
		various treatments.  The difference in priming between each pair of 
		treatments 
		was determined by cross-validation of a Naive Bayes classifier trained
		to classify workers based on the labels they attributed to the first
		image of the final image set. Each panel compares a basis treatment,
		indicated above the panel, to various treatments indicated on the
		abscissa.  We can conclude, with 95\% confidence, that the classifier
		is performing better than chance when $\hat{\theta}_\text{NB}$ 
		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
		the calculation of this confidence threshold.
	}}
}
\end{figure*}

\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

	\caption{ \footnotesize{ 
		Workers were uniformly randomly assigned to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
	}}
	\label{table:1}
\end{table}

@@

\paragraph{Earlier tasks influenced workers' level of specificity.} 
\begin{figure*}
	\centering{
		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
	\caption{\footnotesize{
		\textbf{A}) Percent label composition (culture- vs food-oriented 
		labels) for 
		various images and treatments.  
		\textbf{B}) Relative specificities of treatments
		indicated along the abscissa compared to those indicated above the 
		plot.  The size of the bar indicates how much more specific
		the labels from one treatment are compared to the other, and points 
		toward in the direction of the more specific treatment.
	}}
}
\end{figure*}

@@

To this end, we constructed an ontology from the labels attributed to the 
test images.  The ontology was constructed as a directed acyclic graph, with 
edges pointing from more general labels to more specific ones.
For example, our ontology contains the path \texttt{food} $\to$ 
\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
provide more detail about the construction of the ontology in the 
\textbf{Materials and Methods} section.

@@

@@

\paragraph{Inter-task effects ``wash out'' quickly.}  
\begin{figure}
	\centering{
	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
	\caption{\footnotesize{
		\textbf{A}) Difference in priming between \textsc{AMBG} and 
		$\textsc{CULT}_{img}$ measured based on the accuracy of a Naive Bayes 
		classifier during cross-validation, when trained on labels from the
		test images indicated along the abscissa.
		\textbf{B}) Excess cultural orientation of labels attributed to
		the test images indicated on the abscissa, by workers from
		$\textsc{CULT}_{img}$ relative to those attributed by workers from
		\textsc{AMBG}, calculated using \textbf{Eq. 3}.
	}}
}
\end{figure}
At this point we have 
investigated the inter-task effects induced on only the first image of the 
final image set.  This is because, as mentioned, the effects are strongest on 
for first image.  We now examine how the inter-task effects vary as workers 
proceed through the images in the final set.  Since the final images are the
same for all treatments, it would stand to reason that the inter-task effects
induced by the initial image sets would fade away, being washed out by the
inter-task effects of the final set.

@@

\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
\left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}

@@

\paragraph{Inter-task similarity encourages more specific labels.}
For the next part of the analysis, it will be useful to speak of the
``similarity'' between two image sets. In general, the characterization of 
image content 
is deeply complex and has been approached from the perspectives of 
art\cite{panofsky1939studies,shatford1986analyzing},
psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.
Furthermore, the perception of \textit{similarity} is a particularly subtle 
psychological phenomenon.  For example, a figure $A$ can appear simultaneously
both \textit{more} and \textit{less} similar to an object $C$ than some other 
object $B$.

@@

\begin{table*}
\centering
\begin{tabular}{ l  d  s s s s}

@@

\end{tabular}
\caption{\footnotesize{
	Number of unique labels attributed to each image set, and their
	similarities based on \textbf{Eq. 4} 
}}
\label{table:2}
\end{table*}

@@

This suggests that labeling a series of images that are similar to 
one another might encourage workers to use more specific terminology.
Such a phenomenon would be consistent with the psychological mechanism known 
as \textit{negative priming}.  Negative priming occurs when a person becomes 
desensitized to non-salient stimuli to which she is repeatedly 
exposed.  Consider that workers who initially 
labeled the ambiguous image set had already seen five images showing 
prepared meals once they labeled the first test image.  At that point,
a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
salient, since they do not distinguish the image from those she had seen 
already.

@@

\subsection*{Materials and Methods}
Omitted due to length.  This will be added to supplementary material.

\begingroup
\renewcommand{\chapter}[2]{}
\bibliography{newbib.bib}
\endgroup
\bibliographystyle{plain}

\subsection*{Motivation}
I am near the beginning of my PhD studies, and have joined Derek Ruths' lab 
with the expressed purpose of performing human computation research.
My interests lay at the intersection of game theory, psychology, and 
computation.  The overarching goal for my research relates to group 
decisionmaking, and can be phrased in the following way: ``what are the factors
that influence the social efficiency of collective decisionmaking?'' I
view decisionmaking as the central activity of all social organizations, and 
I view this as a computational process.  My reason for 
wanting to attend the PhD Consortium at HCOMP is threefold.  First, I wish to
discuss my ideas with others, get feedback, and learn more about how the 
community frames such questions, to help me as I finalize my PhD proposal 
into concrete research aims.  Second, I hope to make connections to other 
researchers who are interested in similar research questions.  Finally, I wish
to obtain feedback on a crowdsourcing platform that I have implemented (and
hopefully pique other researcher's interest), which I intend to use in my
research.
\end{document}
